Binomial of sum of Gaussians versus sum of binomial of Gaussians

### 2022-12-12 src/0_checks/bin-gaussian.Rmd
Add xbinom to 0_checks

---
title: "Binomial of sum of Gaussians versus sum of binomial of Gaussians"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background**

  **Task**
---

## Set-up

@@

## Low prevalence setting (disease)

@@

## Probability approximately 1/2 setting (elections)

@@

## Conclusions, things to add

@@

>>>>

---
title: "Binomial of sum of Gaussians versus sum of binomial of Gaussians"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background** Suppose that you take a binomial sample from the average of Gaussians. How different is that to if you aggregated binomial samples from each Gaussian?

  **Task** We simulate data from both models in a setting where $\rho$ is low (disease prevalence) and when $\rho \approx 0.5$ (elections) and compare.
---

# Set-up

@@

# Low probability setting (disease prevalence)

@@

# Probability approximately 1/2 setting (elections)

@@

# Conclusions, things to add

@@

# Original computing environment

```{r}
sessionInfo()
```
